A new simplified manual tour, with application to exploring classification boundaries in high dimensions

### 2022-07-08 paper/paper.Rmd
refininf manual tour explanation

# What is a manual tour? {#sec:method}

An orthonormal basis ($A_{p\times d}$) and a variable id ($m \in \{1, ..., p\}$) to control are provided to initialize a manual tour. A method to update the values of the component of the controlled variable $V_m$ is needed.

@@

# Applications {#sec:examples}

>>>>

# How to construct a manual tour {#sec:method}

A manual tour allows the user to alter the coefficients of one (or more) variables contributing to a $d-D$ projection. The initial ingredients are an orthonormal basis ($A_{p\times d}$) defining the projection of the data, and a variable id ($m \in \{1, ..., p\}$) specifying which coefficient will be changed. A method to update the values of the component of the controlled variable $V_m$ is then needed.

@@

# Application {#sec:examples}

### 2022-07-08 paper/paper.tex
refininf manual tour explanation

\hypertarget{sec:method}{%
\section{What is a manual tour?}\label{sec:method}}

An orthonormal basis (\(A_{p\times d}\)) and a variable id
(\(m \in \{1, ..., p\}\)) to control are provided to initialize a manual
tour. A method to update the values of the component of the controlled
variable \(V_m\) is needed.

@@

\hypertarget{sec:examples}{%
\section{Applications}\label{sec:examples}}

>>>>

\hypertarget{sec:method}{%
\section{How to construct a manual tour}\label{sec:method}}

A manual tour allows the user to alter the coefficients of one (or more)
variables contributing to a \(d-D\) projection. The initial ingredients
are an orthonormal basis (\(A_{p\times d}\)) defining the projection of
the data, and a variable id (\(m \in \{1, ..., p\}\)) specifying which
coefficient will be changed. A method to update the values of the
component of the controlled variable \(V_m\) is then needed.

@@

\hypertarget{sec:examples}{%
\section{Application}\label{sec:examples}}
